\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{kotex}
\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	filecolor=magenta,      
	urlcolor=blue,
}
\usepackage{listings}
\usepackage[super]{nth}
\usepackage[english]{babel}
\graphicspath{{../}}

%% Page Layout %%
\usepackage[left=2.5cm,right=2.5cm,top=3cm,bottom=3cm,a4paper]{geometry}
\setlength{\parskip}{1.5ex}
%
% Homework Details
%   - Title
%   - Due date
%   - Class
%   - Section/Time
%   - Instructor
%   - Author
%

\newcommand{\hwTitle}{Assignment \#3}
\newcommand{\DueDate}{October 22, 2019}
\newcommand{\Semester}{Fall 2019}
\newcommand{\Course}{CS489}
\newcommand{\CourseInstructor}{Prof. Shin Yoo}
\newcommand{\AuthorName}{Inyong Koo}
\newcommand{\StudentID}{20160042}

\newcommand{\Question}{Some people think that computer scientists should take what corresponds to \href{https://en.wikipedia.org/wiki/Hippocratic_Oath}{Hippocratic oath} that physicians take: you can read about the argument \href{https://www.theguardian.com/science/2019/aug/16/mathematicians-need-doctor-style-hippocratic-oath-says-academic-hannah-fry?CMP=Share_iOSApp_Other}{here}. Your assignment is to draft your own version of such an oath.}

%% Headnote, footnote %%
\usepackage{fancyhdr}
\pagestyle{fancy}

\fancyhf{}
\rhead{\StudentID \, \AuthorName}
\lhead{\Semester}
\chead{\Course \, \hwTitle}
\cfoot{\thepage}

\renewcommand{\headrulewidth}{1pt}
\renewcommand{\footrulewidth}{1pt}

\fancypagestyle{titlepagestyle}
{
	\fancyhf{}
	\rhead{Due date: \DueDate}
	\lhead{\Semester}
	\cfoot{\thepage}
	\renewcommand{\footrulewidth}{1pt}
}

\begin{document}
	\title{\vspace{-7ex}\Course \, Computer Ethics \& Social Issues \\ \hwTitle}
	\author{\textbf{My Oath as a Computer Scientist} \\\\ \StudentID \ \AuthorName}
	\date{\hrule}
	%\date{}  % Toggle commenting to test
	
	\maketitle
	
	\thispagestyle{titlepagestyle}
	
	\large \textbf {Q. \Question}
	
	\vspace{3ex}
	
	 
	As a computer scientist and an engineer,
	
	I solemnly pledge to vigorously push forward the frontiers of science and seek application of good cause.
	
	I will research with dignity; I will never yield regarding truth. I will construct my work upon concrete logic and reliable data. I will not violate human rights or and civil liberty during any research procedure. 
	
	I will respect my colleagues; I will respect their intellect and accomplishment. I will actively collaborate with my colleagues and clearly state their contribution.
	
	I will retain humanity. The purpose of my profession is to benefit people's lives. I will always consider the people beneath the numbers and abstractions. The people who get benefit from my work, and more importantly, the people who may get harmed. I will make efforts so that the benefit of my work goes to all people. 
	
	I will be responsible with my work. I will not let my work used on immoral practice. I will maintain and update my work consistently. I will share my works as openly as possible, yet firmly secure the private information and industrial properties.
	
	I make these promises solemnly, freely and upon my honor.
	
	
	\footnotetext{I borrowed expressions from \href{https://en.wikipedia.org/wiki/Declaration_of_Geneva}{declaration of Geneva}, the modern acknowledgement of Hippocratic oath.}
\end{document}